---
title: "I-205 DTA Count Database Map"
author: "Mike Gaunt \n michael.gaunt@wsp.com"
output: html_document


---

<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
suppressMessages({
  suppressWarnings({
    source("./R/mappr_link_extractr.R")
  })
})

suppressMessages({
  suppressWarnings({
    source("./R/mappr_full_data_coverage.R")
  })
})
```

### Description and How to Use  
***
The two maps below depict the data currently available in the I205 DTA Count Database.   
They display the location of the data and the DTA model links which are associated with each data location.    
The first map displays the information by data source, the second by the year the data was acquired - these maps can be navigated to by changing the tab.    

Both maps are interactive and have the same layers.   

* navigation can be performed with your mouse by clicking on the map and dragging
* zoom in and out can be performed with your mouse or with the zoom buttons (top left) 
* layers are turned on or off defualt
* layers can be changed via the "layer box" (top left)   
* base map can be changed via the "layer box" (top left) 

***

## {.tabset}

### Data Source
```{r echo=FALSE, fig.width=15, fig.height=8}
lf_links
```

### Data Acquisition Year
```{r echo=FALSE, fig.width=15, fig.height=8}
lf_links_color
```


```{r echo=FALSE, fig.width=15, fig.height=8}
### Full Subarea Map
# lf
```

































